### 2024-06-15 out/01._Introduction/03._Main_result.tex
corrections

Another key idea for proving \Cref{thm:main} is to consider the area of \(S\) as a function of the cap \(K\). The overestimated area \(\mathcal{A}_1(K)\) in \Cref{fig:a1-upper-bound}, as a function of the cap \(K\), turns out to be \emph{concave} and \emph{quadratic} with respect to \(K\). The space \(\mathcal{K}_\omega\) of all caps \(K\) with a fixed rotation angle \(\omega\) forms a convex space equipped with the convex combination \(c_\lambda(K_1, K_2) = (1 - \lambda) K_1 + \lambda K_2\) defined by the Minkowski sum of convex bodies. Then the Brunn-Minkowski theory on convex bodies \cite{schneider_2013} is used to establish that \(\mathcal{A}_1\) is a quadratic functional on \(\mathcal{K}_\omega\). We use Mamikon’s theorem \autocite{mnatsakanianAnnularRingsEqual1997}, a theorem in classical geometry, to prove that \(\mathcal{A}_1\) concave on \(\mathcal{K}_\omega\) (\Cref{fig:mamikon-sofa}).\footnote{For our application, we rigorously state and prove a generalization (\Cref{thm:mamikon}) of Mamikon’s theorem that is effective on any planar convex body with potentially non-differentiable boundary, which could be of independent interest.} Finally, we introduce a calculus of variation based on the Brunn-Minkowski theory to find a global optimum \(K_1\) of \(\mathcal{A}_1\). \Cref{thm:main} is established by computing the maximum value \(\mathcal{A}_1(K_1) = 1 + \omega^2/2\) of \(\mathcal{A}_1\).

>>>>

Another key idea for proving \Cref{thm:main} is to consider the area of \(S\) as a function of the cap \(K\). The overestimated area \(\mathcal{A}_1(K)\) in \Cref{fig:a1-upper-bound}, as a function of the cap \(K\), turns out to be \emph{concave} and \emph{quadratic} with respect to \(K\). The space \(\mathcal{K}_\omega\) of all caps \(K\) with a fixed rotation angle \(\omega\) forms a convex space equipped with the convex combination \(c_\lambda(K_1, K_2) = (1 - \lambda) K_1 + \lambda K_2\) defined by the Minkowski sum of convex bodies. Then the Brunn-Minkowski theory on convex bodies \cite{schneider_2013} is used to establish that \(\mathcal{A}_1\) is a quadratic functional on \(\mathcal{K}_\omega\). We use Mamikon’s theorem \autocite{mnatsakanianAnnularRingsEqual1997}, a theorem in classical geometry, to prove that \(\mathcal{A}_1\) concave on \(\mathcal{K}_\omega\) (\Cref{fig:mamikon-sofa}).\footnote{For our application, we rigorously state and prove a generalization (\Cref{thm:mamikon}) of Mamikon’s theorem that is effective on any planar convex body with potentially non-differentiable boundary, which could be of independent interest.} Finally, we introduce a calculus of variations based on the Brunn-Minkowski theory to find a global optimum \(K_1\) of \(\mathcal{A}_1\). \Cref{thm:main} is established by computing the maximum value \(\mathcal{A}_1(K_1) = 1 + \omega^2/2\) of \(\mathcal{A}_1\).

### 2024-06-15 out/25._Conditional_upper_bound_A1/00._Preface.tex
corrections

\Cref{sec:calculus-of-variation} shows that the domain \(\mathcal{K}_\omega\) of \(\mathcal{A}_1\), the space of all caps \(K\) with rotation angle \(\omega\), is convex (\Cref{pro:cap-space-convex-space}). Then \Cref{sec:calculus-of-variation} sets up the calculus of variation on a general concave quadratic functional \(f\) on a convex domain \(\mathcal{K}\). In particular, we introduce the notion of \emph{directional derivative} \(Df(K; -)\) of \(f\) (\Cref{def:convex-space-directional-derivative}), and show that any critical point \(K \in \mathcal{K}\) satisfying \(D f(K; -) \leq 0\) is a global maximum (\Cref{thm:quadratic-variation}). This will be used to do the calculus of variation on \(f = \mathcal{A}_1\) with domain \(\mathcal{K} = \mathcal{K}_\omega\).

>>>>

\Cref{sec:calculus-of-variation} shows that the domain \(\mathcal{K}_\omega\) of \(\mathcal{A}_1\), the space of all caps \(K\) with rotation angle \(\omega\), is convex (\Cref{pro:cap-space-convex-space}). Then \Cref{sec:calculus-of-variation} sets up the calculus of variations on a general concave quadratic functional \(f\) on a convex domain \(\mathcal{K}\). In particular, we introduce the notion of \emph{directional derivative} \(Df(K; -)\) of \(f\) (\Cref{def:convex-space-directional-derivative}), and show that any critical point \(K \in \mathcal{K}\) satisfying \(D f(K; -) \leq 0\) is a global maximum (\Cref{thm:quadratic-variation}). This will be used to do the calculus of variations on \(f = \mathcal{A}_1\) with domain \(\mathcal{K} = \mathcal{K}_\omega\).

### 2024-06-15 out/25._Conditional_upper_bound_A1/02._Calculus_of_variation.tex
corrections

We will prove \Cref{thm:main-cap} by optimizing \(\mathcal{A}_1 : \mathcal{K}_\omega \to \mathbb{R}\). Here, we prepare a minimal amount of language needed to execute the calculus of variation to a concave quadratic functional \(f\) on a general convex space \(\mathcal{K}\). Later, we will show that our functional \(f = \mathcal{A}_1\) is concave and quadratic on the cap space \(\mathcal{K} = \mathcal{K}_\omega\), and then deploy the calculus of variation on \(\mathcal{A}_1\).

@@

The \emph{directional derivative} of a quadratic functional \(f\) on a convex space \(\mathcal{K}\) is the key for executing the calculus of variation on \(f\).

>>>>

We will prove \Cref{thm:main-cap} by optimizing \(\mathcal{A}_1 : \mathcal{K}_\omega \to \mathbb{R}\). Here, we prepare a minimal amount of language needed to execute the calculus of variations to a concave quadratic functional \(f\) on a general convex space \(\mathcal{K}\). Later, we will show that our functional \(f = \mathcal{A}_1\) is concave and quadratic on the cap space \(\mathcal{K} = \mathcal{K}_\omega\), and then deploy the calculus of variations on \(\mathcal{A}_1\).

@@

The \emph{directional derivative} of a quadratic functional \(f\) on a convex space \(\mathcal{K}\) is the key for executing the calculus of variations on \(f\).
